\section{Introduction}
The elemental abundances observed throughout the universe are a fingerprint of the formation and evolution of astrophysical objects. Understanding the origin and distribution of these elements requires a robust theoretical framework based on nuclear structure models. The synthesis of elements -- from the lightest nuclei formed during Big Bang nucleosynthesis to the heaviest transuranic elements produced in explosive astrophysical environments -- depends critically on the properties of atomic nuclei.\newline
The foundation for modern nuclear structure theory was laid by the atomic shell model, first introduced by Niels Bohr in 1913. This model, while initially developed for electrons in atoms, inspired the formulation of the nuclear shell model by Maria Goeppert Mayer and J. Hans D. Jensen in 1949. Their key innovation was the inclusion of a significant spin-orbit interaction term in the nuclear mean-field potential. Unlike the atomic case -- where spin-orbit coupling appears as a relatively small fine-structure correction -- in the nuclear shell model, the spin-orbit interaction is of comparable magnitude to the primary energy level gaps and carries an inverted sign. This results in the $j = l + 1/2$ states lying energetically below the $j = l - 1/2$  states.\newline
This critical adjustment enabled the nuclear shell model to accurately reproduce the so-called "magic numbers" (2, 8, 20, 28, 50, 82, and 126), which correspond to closed shells of protons or neutrons associated with exceptional nuclear stability. Notable examples include isotopes such as those of thin (Z = 50) and  lead ( Z = 82), where large energy gaps between filled and unfilled shells lead to enhanced binding energies and structural rigidity.\newline
While the shell model has proven highly successful in describing nuclei close to stability, recent experiments have shown, that the magic shells can be substantially modified in case of exotic species, like $^{32}$Mg \cite{wimmer2010discovery} or $^{28}$O \cite{kanungo2009one}. In case of more heavy regions, experimental data remain scarce, and the shell model must be extended or augmented to account for collective phenomena and configuration mixing. These nuclei play a central role in rapid neutron-capture processes (r-process), which are responsible for the formation of approximately half of the heavy elements beyond iron. In particular, the fate of the r-process path -- its termination via fission and the possible emergence of a predicted "island of stability" in the superheavy region -- depends critically on the structural properties of such exotic nuclei.\newline
This chapter introduces the scientific objectives and research program of the R$^3$B experiment. In particular, we highlight the role of nuclear structure studies in constraining the nuclear equation of state (EOS), especially for highly asymmetric nuclear matter. Nuclear scattering reactions at R$^3$B offer an effective probe of these systems, and their theoretical treatment -- along with a general overview of reaction mechanisms -- will be presented in chapter \ref{sec:reac_model}.

\subsection{R$^3$B Experiment - "The Universe in the Lab"}
\section{Scientific Objectives and Research Program of the R3B Experiment at FAIR}
The R3B experiment (Reactions with Relativistic Radioactive Beams) is a key component of the nuclear astrophysics program at the Facility for Antiproton and Ion Research (FAIR) in Darmstadt and major experiment of the NUSTAR (\textbf{N}uclear \textbf{ST}ructure, \textbf{A}strophysics and \textbf{R}eactions) collaboration~\cite{krucken2005nustar}.\newline
As part of the broader research initiative \textit{"The Universe in the Lab"}, R3B aims to provide a comprehensive understanding of the fundamental nuclear processes that govern the formation of elements in the universe. It seeks to replicate, under controlled laboratory conditions, the extreme environments found in stellar explosions and neutron-star mergers -- astrophysical sites in which rapid nuclear reactions are responsible for the synthesis of the heavy elements~\cite{thielemann2017neutron}.\newline
The central scientific objective of R3B is the investigation of the structure and reaction dynamics of exotic, short-lived nuclei far from the valley of stability, particularly those involved in the rapid neutron-capture process (r-process) and other astrophysical nucleosynthesis pathways~\cite{horowitz2019r}. This includes the determination of key nuclear properties such as masses, lifetimes, decay modes, and reaction cross sections, as well as branching ratios and transition probabilities under conditions similar to those of astrophysical environments.\newline
To address these goals, R3B employs high-intensity, relativistic radioactive ion beams in conjunction with a versatile and high-resolution detectors capable of performing kinematically complete measurements of both incoming and outgoing reaction products. The experimental program covers a wide variety of reaction mechanisms, including fragmentation, Coulomb excitation, knockout, and charge-exchange reactions, as well as inverse kinematics reactions such as (p,n) and (n,p) on liquid hydrogen targets besides on carbon, plastic and lead targets - depending on the experimental focus.\newline
The R3B setup is specifically optimized for operation at beam energies of several hundred~MeV per nucleon. It provides precise tracking and unambiguous particle identification, with excellent resolution in time, energy, and position~\cite{heil2022new}. These capabilities are essential for disentangling complex reaction channels and for extracting high-precision nuclear data that serve as critical input to astrophysical models of nucleosynthesis.\newline
%% EOS study in R3B
Directly related to the scientific objectives at R3B is the exploration of the equation of state (EoS) of asymmetric nuclear matter under extreme conditions. The EoS describes how nuclear matter behaves as a function of parameters such as density, temperature, and isospin asymmetry, and it plays a pivotal role in understanding a wide range of astrophysical phenomena, including the structure and evolution of neutron stars, core-collapse supernovae, and neutron star mergers.


%from ML: In particular, the density dependence of the symmetry energy, a key component of the nuclear EoS, remains poorly constrained at supra-saturation densities. The symmetry energy governs how the energy of nuclear matter changes as the neutron-to-proton ratio varies and has direct consequences for the composition and stability of neutron stars.




Central formula is the equation of states (EOS). We want to study it within a wide range. 
\begin{itemize}
\item in astrophysics NS are herefore of special interest. Measuring their mass and radius -> this relation depends on the EOS. 
\item since NS are highly asymmetric matter (neutrons only) they are a good playground to test the different models. Since they are all consistent at rho0 (real world) they diverge for higher matter asymmetry. 
\item plot of some models
\item formula of tailor expansion of Equation of state
\item at FAIR we want to study  nuclear matter under extreme conditions,highly asymmetric matter. 
\item constraining the symmetry energy
\item this can be done via neutron removal cross section, cite T. Aumann, Bertulani etc.
\item show picture of sensitiveness of this method, shortly mention that L was previously constrained in PREX experiments(give some literature for further readings)
\item the predicted models rely on the input from reaction mechanisms -> 12C+12C good to probe the underlying reaction mechanisms-> one part of the thesis
\end{itemize}
Moreover to study the single particle states of nucleons inside nucleus, exspecially when going toward exotic nuclei-> quasi free scattering experiments.-> refer to the theory of those scattering experiments
This was the first time we had our CALIFA CALORIMETER in its final frame. 
Refer to the application section. \newline
To point out is the pilot experiment we had in 2021 to study fission via qfs. This could have a large impact in the understanding of the dynamics of fission far off the line of stability. \newline
Explain the fission via qfs a little bit more in detail here.\newline
This could explain maybe better the element abundances we have and if there is any island of stability at Z > 126.

